Robust Spectroscopic Inference with Imperfect Models

### 2014-12-17 tex/paper.tex
Moved files

\bibliographystyle{yahapj}
\bibliography{stellarspectra}

>>>>

\bibliographystyle{yahapj}
%\bibliography{stellarspectra}

\begin{thebibliography}{48}
\providecommand\natexlab[1]{#1}
\providecommand\JournalTitle[1]{#1}

\bibitem[{{Allard} {et~al.}(2012){Allard}, {Homeier}, \& {Freytag}}]{allard12}
{Allard}, F., {Homeier}, D., \& {Freytag}, B. 2012,
  \href{http://dx.doi.org/10.1098/rsta.2011.0269}{\JournalTitle{Royal Society
  of London Philosophical Transactions Series A}, 370, 2765}

\bibitem[{{Allard} {et~al.}(2013){Allard}, {Homeier}, {Freytag},
  {Schaffenberger}, \& {Rajpurohit}}]{allard13}
{Allard}, F., {Homeier}, D., {Freytag}, B., {Schaffenberger}, \& {Rajpurohit},
  A.~S. 2013, \JournalTitle{Memorie della Societa Astronomica Italiana
  Supplementi}, 24, 128

\bibitem[{{Astropy Collaboration} {et~al.}(2013){Astropy Collaboration},
  {Robitaille}, {Tollerud}, {Greenfield}, {Droettboom}, {Bray}, {Aldcroft},
  {Davis}, {Ginsburg}, {Price-Whelan}, {Kerzendorf}, {Conley}, {Crighton},
  {Barbary}, {Muna}, {Ferguson}, {Grollier}, {Parikh}, {Nair}, {Unther},
  {Deil}, {Woillez}, {Conseil}, {Kramer}, {Turner}, {Singer}, {Fox}, {Weaver},
  {Zabalza}, {Edwards}, {Azalee Bostroem}, {Burke}, {Casey}, {Crawford},
  {Dencheva}, {Ely}, {Jenness}, {Labrie}, {Lian Lim}, {Pierfederici},
  {Pontzen}, {Ptak}, {Refsdal}, {Servillat}, \& {Streicher}}]{astropy13}
{Astropy Collaboration}, {Robitaille}, T.~P., {Tollerud}, E.~J., {et~al.} 2013,
  \href{http://dx.doi.org/10.1051/0004-6361/201322068}{\JournalTitle{\aap},
  558, A33}

\bibitem[{{Bezanson} {et~al.}(2012){Bezanson}, {Karpinski}, {Shah}, \&
  {Edelman}}]{julia12}
{Bezanson}, J., {Karpinski}, S., {Shah}, V.~B., \& {Edelman}, A. 2012,
  \JournalTitle{ArXiv e-prints},
  \href{http://arxiv.org/abs/1209.5145}{{\sffamily arXiv:1209.5145 [cs.PL]}}

\bibitem[{{Buchhave} {et~al.}(2010){Buchhave}, {Bakos}, {Hartman}, {Torres},
  {Kov\'{a}cs}, {Latham}, {Noyes}, {Esquerdo}, {Everett}, {Howard}, {Marcy},
  {Fischer}, {Johnson}, {Andersen}, {F{\H u}r\'{e}sz}, {Perumpilly},
  {Sasselov}, {Stefanik}, {B\'{e}ky}, {L\'{a}z\'{a}r}, {Papp}, \&
  {S\'{a}ri}}]{buchhave10}
{Buchhave}, L.~A., {Bakos}, G.~A., {Hartman}, J.~D., {et~al.} 2010,
  \href{http://dx.doi.org/10.1088/0004-637X/720/2/1118}{\JournalTitle{\apj},
  720, 1118}

\bibitem[{{Buchhave} {et~al.}(2012){Buchhave}, {Latham}, {Johansen},
  {Bizzarro}, {Torres}, {Rowe}, {Batalha}, {Borucki}, {Brugamyer}, {Caldwell},
  {Bryson}, {Ciardi}, {Cochran}, {Endl}, {Esquerdo}, {Ford}, {Geary},
  {Gilliland}, {Hansen}, {Isaacson}, {Laird}, {Lucas}, {Marcy}, {Morse},
  {Robertson}, {Shporer}, {Stefanik}, {Still}, \& {Quinn}}]{buchhave12}
{Buchhave}, L.~A., {Latham}, D.~W., {Johansen}, A., {et~al.} 2012,
  \href{http://dx.doi.org/10.1038/nature11121}{\JournalTitle{\nat}, 486, 375}

\bibitem[{{Buchhave} {et~al.}(2014){Buchhave}, {Bizzarro}, {Latham},
  {Sasselov}, {Cochran}, {Endl}, {Isaacson}, {Juncher}, \&
  {Marcy}}]{buchhave14}
{Buchhave}, L.~A., {Bizzarro}, M., {Latham}, D.~W., {et~al.} 2014,
  \href{http://dx.doi.org/10.1038/nature13254}{\JournalTitle{\nat}, 509, 593}

\bibitem[{{Cardelli} {et~al.}(1989){Cardelli}, {Clayton}, \&
  {Mathis}}]{cardelli89}
{Cardelli}, J.~A., {Clayton}, G.~C., \& {Mathis}, J.~S. 1989,
  \href{http://dx.doi.org/10.1086/167900}{\JournalTitle{\apj}, 345, 245}

\bibitem[{{Castelli} \& {Kurucz}(2004)}]{castelli04}
{Castelli}, F., \& {Kurucz}, R.~L. 2004, \JournalTitle{ArXiv Astrophysics
  e-prints}, \href{http://arxiv.org/abs/astro-ph/0405087}{{\sffamily
  astro-ph/0405087}}

\bibitem[{{Cushing} {et~al.}(2005){Cushing}, {Rayner}, \& {Vacca}}]{cushing05}
{Cushing}, M.~C., {Rayner}, J.~T., \& {Vacca}, W.~D. 2005,
  \href{http://dx.doi.org/10.1086/428040}{\JournalTitle{\apj}, 623, 1115}

\bibitem[{{Cushing} {et~al.}(2004){Cushing}, {Vacca}, \& {Rayner}}]{cushing04}
{Cushing}, M.~C., {Vacca}, W.~D., \& {Rayner}, J.~T. 2004,
  \href{http://dx.doi.org/10.1086/382907}{\JournalTitle{\pasp}, 116, 362}

\bibitem[{{Eisenstein} {et~al.}(2006){Eisenstein}, {Liebert}, {Harris},
  {Kleinman}, {Nitta}, {Silvestri}, {Anderson}, {Barentine}, {Brewington},
  {Brinkmann}, {Harvanek}, {Krzesi\'{n}ski}, {Neilsen}, {Long}, {Schneider}, \&
  {Snedden}}]{eisenstein06}
{Eisenstein}, D.~J., {Liebert}, J., {Harris}, H.~C., {et~al.} 2006,
  \href{http://dx.doi.org/10.1086/507110}{\JournalTitle{\apjs}, 167, 40}

\bibitem[{{F{\H{u}}r\'{e}sz}(2008)}]{furesz08}
{F{\H{u}}r\'{e}sz}, G. 2008

\bibitem[{{Fischer} \& {Valenti}(2005)}]{fischer05}
{Fischer}, D.~A., \& {Valenti}, J. 2005,
  \href{http://dx.doi.org/10.1086/428383}{\JournalTitle{\apj}, 622, 1102}

\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
  {Goodman}}]{foreman-mackey13}
{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013,
  \href{http://dx.doi.org/10.1086/670067}{\JournalTitle{\pasp}, 125, 306}

\bibitem[{Foreman-Mackey {et~al.}(2014)Foreman-Mackey, Price-Whelan, Ryan,
  Rice, Smith, Barbary, Hogg, \& Brewer}]{foreman-mackey14}
Foreman-Mackey, D., Price-Whelan, A., Ryan, G., {et~al.}
  \href{http://dx.doi.org/10.5281/zenodo.10598}{2014}

\bibitem[{Gelman {et~al.}(2013)Gelman, Carlin, Stern, Dunson, Vehtari, \&
  Rubin}]{gelman13}
Gelman, A., Carlin, J., Stern, H., {et~al.} 2013, {Bayesian Data Analysis,
  Third Edition}, {Chapman \& Hall/CRC Texts in Statistical Science} (Taylor \&
  Francis)

\bibitem[{{Gray}(1994)}]{gray94}
{Gray}, D.~F. 1994,
  \href{http://dx.doi.org/10.1086/133502}{\JournalTitle{\pasp}, 106, 1248}

\bibitem[{{Gray}(2008)}]{gray08}
---. 2008, {The Observation and Analysis of Stellar Photospheres}

\bibitem[{{Habib} {et~al.}(2007){Habib}, {Heitmann}, {Higdon}, {Nakhleh}, \&
  {Williams}}]{habib07}
{Habib}, S., {Heitmann}, K., {Higdon}, D., {Nakhleh}, C., \& {Williams}, B.
  2007,
  \href{http://dx.doi.org/10.1103/PhysRevD.76.083503}{\JournalTitle{\prd}, 76,
  083503}

\bibitem[{{Hauschildt} {et~al.}(1999){Hauschildt}, {Allard}, \&
  {Baron}}]{hauschildt99}
{Hauschildt}, P.~H., {Allard}, F., \& {Baron}, E. 1999,
  \href{http://dx.doi.org/10.1086/306745}{\JournalTitle{\apj}, 512, 377}

\bibitem[{{Heitmann} {et~al.}(2009){Heitmann}, {Higdon}, {White}, {Habib},
  {Williams}, {Lawrence}, \& {Wagner}}]{heitmann09}
{Heitmann}, K., {Higdon}, D., {White}, M., {et~al.} 2009,
  \href{http://dx.doi.org/10.1088/0004-637X/705/1/156}{\JournalTitle{\apj},
  705, 156}

\bibitem[{{Howard} {et~al.}(2010){Howard}, {Marcy}, {Johnson}, {Fischer},
  {Wright}, {Isaacson}, {Valenti}, {Anderson}, {Lin}, \& {Ida}}]{howard10}
{Howard}, A.~W., {Marcy}, G.~W., {Johnson}, J.~A., {et~al.} 2010,
  \href{http://dx.doi.org/10.1126/science.1194854}{\JournalTitle{Science}, 330,
  653}

\bibitem[{{Husser} {et~al.}(2013){Husser}, {Wende-von Berg}, {Dreizler},
  {Homeier}, {Reiners}, {Barman}, \& {Hauschildt}}]{husser13}
{Husser}, T.-O., {Wende-von Berg}, S., {Dreizler}, S., {et~al.} 2013,
  \href{http://dx.doi.org/10.1051/0004-6361/201219058}{\JournalTitle{\aap},
  553, A6}

\bibitem[{{Ivezi\'{c}} {et~al.}(2013){Ivezi\'{c}}, {Connolly}, {VanderPlas}, \&
  {Gray}}]{ivezic13}
{Ivezi\'{c}}, {\.Z}., {Connolly}, A., {VanderPlas}, J., \& {Gray}, A. 2013,
  {Statistics, Data Mining, and Machine Learning in Astronomy}

\bibitem[{{Johnson} {et~al.}(2007){Johnson}, {Butler}, {Marcy}, {Fischer},
  {Vogt}, {Wright}, \& {Peek}}]{johnson07}
{Johnson}, J.~A., {Butler}, R.~P., {Marcy}, G.~W., {et~al.} 2007,
  \href{http://dx.doi.org/10.1086/521720}{\JournalTitle{\apj}, 670, 833}

\bibitem[{{Joshi} {et~al.}(2009){Joshi}, {Pollacco}, {Collier Cameron},
  {Skillen}, {Simpson}, {Steele}, {Street}, {Stempels}, {Christian}, {Hebb},
  {Bouchy}, {Gibson}, {H\'{e}brard}, {Keenan}, {Loeillet}, {Meaburn}, {Moutou},
  {Smalley}, {Todd}, {West}, {Anderson}, {Bentley}, {Enoch}, {Haswell},
  {Hellier}, {Horne}, {Irwin}, {Lister}, {McDonald}, {Maxted}, {Mayor},
  {Norton}, {Parley}, {Perrier}, {Pont}, {Queloz}, {Ryans}, {Smith}, {Udry},
  {Wheatley}, \& {Wilson}}]{joshi09}
{Joshi}, Y.~C., {Pollacco}, D., {Collier Cameron}, A., {et~al.} 2009,
  \href{http://dx.doi.org/10.1111/j.1365-2966.2008.14178.x}{\JournalTitle{\mnras},
  392, 1532}

\bibitem[{{Koleva} {et~al.}(2009){Koleva}, {Prugniel}, {Bouchard}, \&
  {Wu}}]{koleva09}
{Koleva}, M., {Prugniel}, P., {Bouchard}, A., \& {Wu}, Y. 2009,
  \href{http://dx.doi.org/10.1051/0004-6361/200811467}{\JournalTitle{\aap},
  501, 1269}

\bibitem[{{Kurucz}(1993)}]{kurucz93}
{Kurucz}, R.~L. 1993, {SYNTHE spectrum synthesis programs and line data}

\bibitem[{{Mann} {et~al.}(2013){Mann}, {Gaidos}, \& {Ansdell}}]{mann13}
{Mann}, A.~W., {Gaidos}, E., \& {Ansdell}, M. 2013,
  \href{http://dx.doi.org/10.1088/0004-637X/779/2/188}{\JournalTitle{\apj},
  779, 188}

\bibitem[{{Nidever} {et~al.}(2012){Nidever}, {Zasowski}, {Majewski}, {Bird},
  {Robin}, {Martinez-Valpuesta}, {Beaton}, {Sch\"{o}nrich}, {Schultheis},
  {Wilson}, {Skrutskie}, {O'Connell}, {Shetrone}, {Schiavon}, {Johnson},
  {Weiner}, {Gerhard}, {Schneider}, {Allende Prieto}, {Sellgren}, {Bizyaev},
  {Brewington}, {Brinkmann}, {Eisenstein}, {Frinchaboy}, {Elia Garc\'{\i}a
  P\'{e}rez}, {Holtzman}, {Hearty}, {Malanushenko}, {Malanushenko}, {Muna},
  {Oravetz}, {Pan}, {Simmons}, {Snedden}, \& {Weaver}}]{nidever12}
{Nidever}, D.~L., {Zasowski}, G., {Majewski}, S.~R., {et~al.} 2012,
  \href{http://dx.doi.org/10.1088/2041-8205/755/2/L25}{\JournalTitle{\apjl},
  755, L25}

\bibitem[{{Paxton} {et~al.}(2011){Paxton}, {Bildsten}, {Dotter}, {Herwig},
  {Lesaffre}, \& {Timmes}}]{paxton11}
{Paxton}, B., {Bildsten}, L., {Dotter}, A., {et~al.} 2011,
  \href{http://dx.doi.org/10.1088/0067-0049/192/1/3}{\JournalTitle{\apjs}, 192,
  3}

\bibitem[{{Rajpurohit} {et~al.}(2014){Rajpurohit}, {Reyl\'{e}}, {Allard},
  {Scholz}, {Homeier}, {Schultheis}, \& {Bayo}}]{rajpurohit14}
{Rajpurohit}, A.~S., {Reyl\'{e}}, C., {Allard}, F., {et~al.} 2014,
  \href{http://dx.doi.org/10.1051/0004-6361/201322881}{\JournalTitle{\aap},
  564, A90}

\bibitem[{{Rajpurohit} {et~al.}(2010){Rajpurohit}, {Reyl\'{e}}, {Schultheis},
  \& {Allard}}]{rajpurohit10}
{Rajpurohit}, A.~S., {Reyl\'{e}}, C., {Schultheis}, M., \& {Allard}, F. 2010,
  in {SF2A-2010: Proceedings of the Annual meeting of the French Society of
  Astronomy and Astrophysics}, ed. S.~{Boissier}, M.~{Heydari-Malayeri},
  R.~{Samadi}, \& D.~{Valls-Gabaud}, 275

\bibitem[{Rasmussen \& Williams(2005)}]{rasmussen05}
Rasmussen, C.~E., \& Williams, C. K.~I. 2005, {Gaussian Processes for Machine
  Learning (Adaptive Computation and Machine Learning)} (The MIT Press)

\bibitem[{{Rayner} {et~al.}(2009){Rayner}, {Cushing}, \& {Vacca}}]{rayner09}
{Rayner}, J.~T., {Cushing}, M.~C., \& {Vacca}, W.~D. 2009,
  \href{http://dx.doi.org/10.1088/0067-0049/185/2/289}{\JournalTitle{\apjs},
  185, 289}

\bibitem[{{Rayner} {et~al.}(2003){Rayner}, {Toomey}, {Onaka}, {Denault},
  {Stahlberger}, {Vacca}, {Cushing}, \& {Wang}}]{rayner03}
{Rayner}, J.~T., {Toomey}, D.~W., {Onaka}, P.~M., {et~al.} 2003,
  \href{http://dx.doi.org/10.1086/367745}{\JournalTitle{\pasp}, 115, 362}

\bibitem[{{Reid} {et~al.}(1995){Reid}, {Hawley}, \& {Gizis}}]{reid95}
{Reid}, I.~N., {Hawley}, S.~L., \& {Gizis}, J.~E. 1995,
  \href{http://dx.doi.org/10.1086/117655}{\JournalTitle{\aj}, 110, 1838}

\bibitem[{{Rojas-Ayala} {et~al.}(2010){Rojas-Ayala}, {Covey}, {Muirhead}, \&
  {Lloyd}}]{rojas-ayala10}
{Rojas-Ayala}, B., {Covey}, K.~R., {Muirhead}, P.~S., \& {Lloyd}, J.~P. 2010,
  \href{http://dx.doi.org/10.1088/2041-8205/720/1/L113}{\JournalTitle{\apjl},
  720, L113}

\bibitem[{{Rojas-Ayala} {et~al.}(2012){Rojas-Ayala}, {Covey}, {Muirhead}, \&
  {Lloyd}}]{rojas-ayala12}
---. 2012,
  \href{http://dx.doi.org/10.1088/0004-637X/748/2/93}{\JournalTitle{\apj}, 748,
  93}

\bibitem[{{Sch\"{o}nrich} \& {Bergemann}(2013)}]{schoenrich13}
{Sch\"{o}nrich}, R., \& {Bergemann}, M. 2013, \JournalTitle{ArXiv e-prints},
  \href{http://arxiv.org/abs/1311.5558}{{\sffamily arXiv:1311.5558
  [astro-ph.SR]}}

\bibitem[{{Shkedy} {et~al.}(2007){Shkedy}, {Decin}, {Molenberghs}, \&
  {Aerts}}]{shkedy07}
{Shkedy}, Z., {Decin}, L., {Molenberghs}, G., \& {Aerts}, C. 2007,
  \href{http://dx.doi.org/10.1111/j.1365-2966.2007.11508.x}{\JournalTitle{\mnras},
  377, 120}

\bibitem[{{Sneden}(1973)}]{sneden73}
{Sneden}, C.~A. 1973, PhD thesis, The University of Texas at Austin.

\bibitem[{{Tonry} \& {Davis}(1979)}]{tonry79}
{Tonry}, J., \& {Davis}, M. 1979,
  \href{http://dx.doi.org/10.1086/112569}{\JournalTitle{\aj}, 84, 1511}

\bibitem[{{Torres} {et~al.}(2012){Torres}, {Fischer}, {Sozzetti}, {Buchhave},
  {Winn}, {Holman}, \& {Carter}}]{torres12}
{Torres}, G., {Fischer}, D.~A., {Sozzetti}, A., {et~al.} 2012,
  \href{http://dx.doi.org/10.1088/0004-637X/757/2/161}{\JournalTitle{\apj},
  757, 161}

\bibitem[{{Vacca} {et~al.}(2003){Vacca}, {Cushing}, \& {Rayner}}]{vacca03}
{Vacca}, W.~D., {Cushing}, M.~C., \& {Rayner}, J.~T. 2003,
  \href{http://dx.doi.org/10.1086/346193}{\JournalTitle{\pasp}, 115, 389}

\bibitem[{{Valenti} \& {Piskunov}(1996)}]{valenti96}
{Valenti}, J.~A., \& {Piskunov}, N. 1996, \JournalTitle{\aaps}, 118, 595

\bibitem[{{Zucker} {et~al.}(2012){Zucker}, {de Silva}, {Freeman},
  {Bland-Hawthorn}, \& {Hermes Team}}]{zucker12}
{Zucker}, D.~B., {de Silva}, G., {Freeman}, K., {Bland-Hawthorn}, J., \&
  {Hermes Team}. 2012, in {Astronomical Society of the Pacific Conference
  Series}, Vol. 458, {Galactic Archaeology: Near-Field Cosmology and the
  Formation of the Milky Way}, ed. W.~{Aoki}, M.~{Ishigaki}, T.~{Suda},
  T.~{Tsujimoto}, \& N.~{Arimoto}, 421

\end{thebibliography}
